Supplementary Information

### 2020-12-28 doc/manuscript/MEE_manuscript.Rmd
minor updates

To test for $year$ effects, we limited the analysis of each species to years for which the $DBH$ range represented by at least 3 individuals spanned at least half the total range of that species, dropping species entirely if < 30 years met this criteria. 
We then ran models as described above, including a  first-order linear effect of $year$.
To verify that GLS model trends for $year$ were real, as opposed to an artifact of inherent covariation between $DBH$ and $year$ within each core, we separately analyzed $DBH$-growth relationships by decade (Appendix `r decadal_analysis_appendix`). 
For simplicity and consistency with previous literature, we present only the models with $BAI$ as the growth metric, noting that responses were similar across metrics.

>>>>

To test for $year$ effects, we limited the analysis to species with reasonable coverage of an $DBH$ x `year` matrix.
Specifically, we required that the species be represented by cores from  $\ge$ 3 trees spanning  $\ge$ 40% the total $DBH$ range for $\ge 2/3$ of the total time range analyzed. 
Species that failed to meet this criteria (n= **N**) were excluded from this analysis.
We then ran models as described above, including a  first-order linear effect of $year$.
To verify that GLS model trends for $year$ were real, as opposed to an artifact of inherent covariation between $DBH$ and $year$ within each core, we separately analyzed $DBH$-growth relationships by decade (Appendix `r decadal_analysis_appendix`). 
For simplicity and consistency with previous literature, we present only the models with $BAI$ as the growth metric, noting that responses were similar across metrics.

### 2020-12-28 doc/manuscript/MEE_manuscript_SI.Rmd
minor updates

\newpage
## `r site_details_legend` 
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/site_details.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE,   escape = F)%>%
  column_spec(2, width = "3cm") %>%
  column_spec(5, width = "2cm") %>%
  column_spec(6, width = "2cm") %>%
  column_spec(7, width = "1.5cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
* Refers to approximate period during which woody growth ceases (dry season in the tropics, winter for temperate and boreal sites).

>>>>

\newpage
## `r site_details_legend` 
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/site_details.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE,   escape = F)%>%
  column_spec(2, width = "3cm") %>%
  column_spec(5, width = "2cm") %>%
  column_spec(6, width = "2cm") %>%
  column_spec(7, width = "1.5cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
*Refers to approximate period during which woody growth ceases (dry season in the tropics, winter for temperate and boreal sites).
